Tuning Low Frequency Pulsar Searching with an Artificial Pulsar Device

### 2020-12-27 ms.tex
Updates from Overleaf

\subsection{Important Approximations that We Make}
The purpose of this work is to present a method of tuning the search of pulsars in low frequency radio band, which is composed of signal receiving/recording and signal detection.
Dedispersion is an important step in the signal detection stage.
According to e.g., \citet{2012hpa..book.....L}, it is possible to perform either coherent dedispersion or incoherent dedispersion. The former works on raw baseband data and the latter works on channelized filterbank data. 
The main different between these two category of dedispersion methods is whether phase information is kept in the input data.
In order to enable the generated signal suitable to both category of dedispersion methods, we have to ensure that the phase information is treated with caution.
Considering that fact that the dispersion caused by ISM can cause delays of different frequencies in low frequency band to reach at most $10^2$ s time scale, computing the dispersed pulsar signal online without necessary approximation is infeasible.

>>>>

\subsection{Important Approximations that We Make}
The purpose of this work is to present a method of tuning the search of pulsars in low frequency radio band, which is composed of signal receiving/recording and signal detection.
Dedispersion is an important step in the signal detection stage.
According to e.g., \citet{2012hpa..book.....L}, it is possible to perform either coherent dedispersion or incoherent dedispersion. The former works on raw baseband data and the latter works on channelized filterbank data. 
The main different between these two category of dedispersion methods is whether phase information is kept in the input data.
In order to enable the generated signal suitable to both category of dedispersion methods, we have to ensure that the phase information is treated with caution.
Considering the fact that the dispersion caused by ISM can cause delays of different frequencies in low frequency band to reach at most $10^2$ s time scale, computing the dispersed pulsar signal online without necessary approximation is inefficient.
